---
title: "Principal Components Analysis"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(car)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.eval = TRUE)
```


## Motivation

Lets consider this dataset, it has highly correlated variables. We would like to understand the relationship between variables or relationship with response and variables


---
# Eigen Values and Vectors

```{r , echo = FALSE, eval = TRUE}
indata <- read.csv("data/nyse_wrr_stocks.csv")
corMat = cor(indata)
```

```{r ,echo =TRUE, eval = TRUE}
head(indata, 2)
```

```{r,  eval = TRUE}
eigenRes = eigen(corMat)
```

#### *Eigenvalues*
```{r , eval = TRUE}
eigenRes$values
```

#### *EigenVectors*
```{r , eval = TRUE}
eigenRes$vectors
```
---
# Determining Principal Components

--

There is no universal objective way to determine the number of principal components, typically it is subjected aided by one of the following:
1. the amount of total sample variance explained
2. relative sizes of eigen values
3. subject-matter interpretations
4. point of bend in the scree plot

--

</br>

```{r pve , eval = FALSE}
PVE <- eigenRes$values / sum(eigenRes$values)
# Percent variance explained
PVE
#Cumulative percent variance explained
cumsum(PVE)
```
---
# Scree Plot
#### * Plot of magnitude of the eigen value on the y-axis versus its index on the x-axis. 
#### * Look for an elbow (or a bend) in the scree plot. 
#### * The elbow occurs at 3 and since the first three components explain 87% of the sample variance.

.pull-left[
```{r scree, echo=FALSE}
# PVE (aka scree) plot
corMat = cor(indata)
eigenRes = eigen(corMat)
PVE <- eigenRes$values / sum(eigenRes$values)
PVEplot <- qplot(c(1:5), PVE) + 
  geom_line() + 
  xlab("Principal Component") + 
  ylab("PVE") +
  ggtitle("Scree Plot") +
  ylim(0, 1)

PVEplot
```
]
.pull-right[
```{r echo = FALSE}
# Cumulative PVE plot
cumPVE <- qplot(c(1:5), cumsum(PVE)) + 
  geom_line() + 
  xlab("Principal Component") + 
  ylab(NULL) + 
  ggtitle("Cumulative Scree Plot") +
  ylim(0,1)

cumPVE
#grid.arrange(PVEplot, cumPVE, ncol = 2)
```
]
---
# Interpreting Loadings
```{r loadings , eval=FALSE}
#plot number of eigen values that need to be selected
evecs = eigenRes$vectors[,1:3]
colnames(evecs) = c("e1", "e2", "e3")
row.names(evecs) = colnames(indata)
evecs
```

```{r eval=TRUE, echo=FALSE}
#plot number of eigen values that need to be selected
evecs = eigenRes$vectors[,1:3]
colnames(evecs) = c("e1", "e2", "e3")
row.names(evecs) = colnames(indata)
evecs %>% knitr::kable()
```

Interpretation: The first component is roughly equally weighted sum of the five stocks. This can be the general market component.

The second component represents a contrast between bank stocks {JPM, Citibank, WellFargo} and the oil stocks {Royal Dutch, Exxon}. This can be interpreted as industry component.
---
# Principal Components Score
The sample principal components are defined as those linear combinations which have maximum sample variance.
If we project the 103 data points onto the first eigen vectors , the projected values are called the first principal component
```{r princomp, eval=FALSE}
PC1 <- as.matrix(scaled_indata) %*% evecs[,1]
PC2 <- as.matrix(scaled_indata) %*% evecs[,2]
PC <- data.frame(Week = row.names(indata), PC1, PC2)
head(PC)
```
---
# Visualize 

### Plot two principal components
```{r viz, eval=FALSE}
ggplot(PC, aes(PC1, PC2)) + 
  modelr::geom_ref_line(h = 0) +
  modelr::geom_ref_line(v = 0) +
  geom_text(aes(label = Week), size = 3) +
  xlab("First Principal Component") + 
  ylab("Second Principal Component") + 
  ggtitle("First Two Principal Components of Stock Return Data")
```