---
title: "Review R Introduction"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
# devtools::install_github("rstudio-education/gradethis")
library(gradeR)
library(testthat) 
# devtools::install_github("rundel/learnrhash")
library(learnrhash)

library(Hmisc) #useful for describing the dataset

tutorial_options(exercise.timelimit = 60, exercise.checker = gradethis::grade_learnr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

### Learning Goal
This is an *ungraded* tutorial. The objective is to review some key concepts covered in the R-intro website provided in the reference readings, sections 1 - 4. It is not meant to be exhaustive in coverage. 

### Reference Readings

https://cran.r-project.org/doc/manuals/r-release/R-intro.html

### First, lets know how to get help

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to get correct syntax for function read.csv from the documentation

```{r exercise_help, exercise= TRUE, exercise.eval=TRUE}

```


```{r exercise_help-check}
grade_result(
  pass_if(~ identical(.result, help(read.csv)), "Good job!")
)
```

Two handy functions for getting or setting the filepath to the working directory are getwd() and setwd(). Do check the documentation by running help(getwd) and help(setwd)


## Reading data into R
There are multiple ways to import data in R. You can check out more comprehensive manual here: https://cran.r-project.org/doc/manuals/r-release/R-data.pdf

Base R comes with a selection of built-in datasets. This can be handy to get started quickly on learning methods in R. To see a list, run data().

```{r inbuilt_data, exercise = TRUE}
data()
```

In this class we will mostly work with built-in datasets or data available in csv format either stored locally or online.

For this tutorial please import the data located here: "https://raw.githubusercontent.com/guptashilpa/FA20-ISE201/master/Data/faithful_data.csv" and store it into a variable in_data

The data consists of waiting time between eruptions and the duration of the eruption for the Old Faithful geyser in Yellowstone National Park, Wyoming, USA.
```{r read_data, exercise = TRUE, exercise.eval=TRUE}

```

You could also run the View(in_data) to view the data table. Works in RStudio IDE.


```{r read_data-check}
grade_result(
  pass_if(~ identical(.result, sum(vec3)), "Good job!")
)
```

## Data Checks
Please check if in_data is a data.frame
```{r check_data, exercise = TRUE}

```


Print the first 5 rows of the in_data
```{r print_data, exercise = TRUE}

```

Does the first column providing any useful information? If not, delete it
```{r drop_col, exercise =TRUE}

```
There are multiple ways the data can be corrupted or missing. The missing values are typically represented as NA. 

Please check if there are missing values in samplevec. Could you print the indices of the missing values.
```{r check_miss, exercise = TRUE}
samplevec = c(1:5, NA, 7:10, NA)

```
You can also 
<div id="read_data-hint">
**Hint:** You may want to check this out https://cran.r-project.org/doc/manuals/r-release/R-intro.html#Reading-data-from-files
Or help(read.csv)
</div>

<div id="check_data-hint">
**Hint:** You may want to check this out https://cran.r-project.org/doc/manuals/r-release/R-intro.html#Reading-data-from-files
Or help(is.data.frame)
</div>

<div id="print_data-hint">
**Hint:** You may want to check this out https://cran.r-project.org/doc/manuals/r-release/R-intro.html#Reading-data-from-files
Or help(head)
</div>

<div id="check_miss-hint">
**Hint:** You may want to check this out https://uc-r.github.io/missing_values
Or help(is.na) and help(which)
</div>

<div id="drop_col-hint">
**Hint:** You may want to check this out https://cran.r-project.org/doc/manuals/r-release/R-intro.html#Index-vectors
Or https://stackoverflow.com/questions/4605206/drop-data-frame-columns-by-name
</div>

## Data Summary

It is usually a good idea to understand the variables and visually inspect the data 

Print the key statistics of the variables
```{r data_summary, exercise = TRUE}

```

Plot a scatter plot of data
```{r data_plot, exercise = TRUE}

```

<div id="data_summary-hint">
**Hint:** You may want to check this out help(summary)
</div>

<div id="data_plot-hint">
**Hint:** You may want to check this out help(plot)
</div>

## Quiz

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```


## Wrap Up & Submit

Congratulations, we hope you enjoyed reviewing what we've learned so far!


```{r context="server"}
learnrhash::encoder_logic()
```

```{r encode, echo=FALSE}
# learnrhash::encoder_ui(url = "https://forms.gle/nmsi2WfR2zGp2C5f9")
learnrhash::encoder_ui(
  ui_before = shiny::div(
    "If you have completed this tutorial and are happy with all of your",
    "solutions, please click the button below to generate your hash and",
    "submit it using the following form:",
    shiny::tags$br()
  ), 
  ui_after = learnrhash::iframe_ui(
    src = "https://docs.google.com/forms/d/e/1FAIpQLScBHgBdxRxmm5uakvK1NU4pmD9TDpU-RDkrEXcXog9nuc-RHQ/viewform?embedded=true" 
    , width="640px", height= "300px", frameborder="0", marginheight="0", marginwidth="0"
  )
)
```
