---
title: "Learning to work with Open Gov Data - Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Data Background

Before begining any analysis, it is prudent to get as much information about how the data was collected, when it was collected and for what purpose was the data collected. 

In this tutorial, we will walk you through the steps of reading, preprocessing data obtained from data.gov


### Reading Data

For our tutorial, we will demonstrate using functions from `tidyverse` package. In order to achieve that, we need to laod in the package. Use the code chunck below to import the package

```{r import-library, exercise=TRUE}
library(...)
```

Write the R code required to read in the data using `read_csv()`. The data is available at this location `INCLUDE LOCATION`


```{r read-data, exercise=TRUE}

```

Next step is to check for the data size and also quick quality check to ensure how many, if any missing values or duplicate rows are present in the data

### Data Size

What is the size of data? How many observations and how many variables? We will use the function `dim()`
*Print the number of rows and number of columns in the dataset*

```{r data-dim, exercise=TRUE, exercise.lines = 5}

```

### Quick quality check

How many missing values? What are the variable types? 

```{r data-check, exercise=TRUE, exercise.lines = 5}

```

## Descriptive Data

How many columns are categorical and numeric?

```{r data-types, exercise=TRUE, exercise.lines = 5}

```
For numeric columns, what do the summary statistics for central tendency and spread looks like?

```{r num-stats, exercise=TRUE, exercise.lines = 5}

```
For categorical columns, what is the distribution across caetgories and the mode value.

```{r cat-stats, exercise=TRUE, exercise.lines = 5}

```
## Data Visualization

### Distribution
To ascertain distribution, we will use histogram for numeric variables and bar plots for categorical variables

```{r hist, exercise=TRUE, exercise.lines = 5}

```

```{r bar, exercise=TRUE, exercise.lines = 5}

```

```{r boxplot, exercise=TRUE, exercise.lines = 5}

```
### Relationship
Scatter plot 

```{r scatter, exercise=TRUE, exercise.lines = 5}

```
Correlation coefficient

```{r cor-coef, exercise=TRUE, exercise.lines = 5}

```
###


## Hypothesis Testing [Need to update]


### Exercise with Hint

*Here's an exercise where the chunk is pre-evaluated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

## About

This tutorial has been prepared by Tai Shih under the guidance of Dr. Shilpa Gupta as part of the UROP. Please contact shilpa.gupta@sjsu.edu for questions or comments. 

